---
title: "Testing Block Floyd-Warshall"
author: "Charles Zheng"
date: "05/11/2015"
output: html_document
---

# Requirements

The following libraries must be installed:
```{r}
library(Rcpp)
library(pracma)
```

# Introduction

See `apsp.Rmd`.  Code from previous:

```{r}
library(Rcpp)
cppFunction('
NumericMatrix minplus(NumericMatrix Ar, NumericMatrix Br) {
  int n = Ar.nrow();
  int l = Ar.ncol();
  int m = Br.ncol();
  NumericMatrix ans(n, m);
  for (int i = 0; i < n; i++) {
    for (int j = 0; j < m; j++) {
      for (int k = 0; k < l; k++) {
        double x = Ar(i, k) + Br(k, j);
        if (x < ans(i, j) || k == 0) {
          ans(i, j) = x;
        }
      }
    }
  }
  return ans;
}
'
)

block_fw <- function(a, k, l) {
  n <- dim(a)[1]
  m <- ceiling(n/k)
  for (main_it in 1:l) {
    for (i in 1:m) {
      Bi <- a[, ((i-1) * k + 1):min(n, i * k), drop = FALSE]
      a <- pmin(a, minplus(Bi, t(Bi)))
    }
  }
  a
}
```

# Problem

Given that block Floyd-Warshall is not guaranteed to compute the APSP matrix exactly, what kind of approximation properties does it have, assuming that the input matrix is pre-shuffled?

Start by looking at a *difficult case* for the all-pairs-shortest-paths problem: a line graph!

```{r}
line_graph <- function(n, shuffle = TRUE) {
  A <- matrix(Inf, n, n)
  A[abs(row(A)-col(A)) == 1] <- 1
  diag(A) <- 0
  if (shuffle) {
    perm <- sample(n, n)
    A <- A[perm, perm]
  }
  A
}
line_graph(6, FALSE)
```

# Block FW on line graph

Generate the line graph and the correct solution (using Floyd-Warshall).

```{r}
n <- 100
A <- line_graph(n)
A_fw <- block_fw(A, 1, 1)
```

Try block FW with $k = 2$ and $L = 2$.

```{r}
A_bfw <- block_fw(A, 2, 2)
sum(A_bfw == Inf)
sum(A_bfw != A_fw)
```

Is it exact?

# Line graph simulations

What is the probability of exact recovery depending on $k$ and $L$?
For each $k$, find the minimum $L$ which gives exact recovery.

```{r}
find_L <- function(n, k) {
  A <- line_graph(n)
  L <- k
  A_fw <- block_fw(A, 1, 1)
  flag <- TRUE
  while (flag) {
    A_bfw <- block_fw(A, k, L)
    flag <- (sum(A_bfw != A_fw) == 0)
    # to be contd
  }
}
```
